Long name of the paper

### 2018-06-11 anzjs2018/anzjs2018.tex
Wordssss :book:

Over the years, advances in computing power have enabled new
modeling approaches,
such as support vector machines \citep

>>>>

Over the years, advances in computing power have enabled new
modeling approaches,
such as support vector machines \citep{Yu_2006},
artificial neural networks \citep{Yu_2011},
and more recently particle filters \citep{Hans_2015}.
